---
title: "Ex.7Chapter8"
author: "Ntoulmperis Michail"
date: "26/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First we load the libraries and the assign the data set to "df"
```{r, warning = FALSE, message = FALSE}
library(tree)
library(randomForest)
library(MASS)
df <- Boston
```
## Then we proceed to split the data set into train and test
```{r}
set.seed(1)

train <-sample(1:nrow(df),nrow(df)*0.7)

df.train<-df[train,-14]

df.test<-df[!train,-14]

y.train<-df[train,14]

y.test<- df[!train,14]
```

Now we are going to build 5 models with the same number of trees.
We are going to see that is doesnt affect the MSe. Regarging the mtry we are 
going to try and compute a diffrent one for each by dividing the collumes with
diffrent numbers. This way we are going to see how the model is affected by how
many variables we include in it

```{r}
rf1<-randomForest(df.train, y.train,xtest = df.test, ytest = y.test,ntree=500,mtry=(ncol(df.train))^(0.5))
  
rf2<-randomForest(df.train, y.train,xtest = df.test, ytest = y.test,ntree=500,mtry=(ncol(df.train))/2)
  
rf3<-randomForest(df.train, y.train,xtest = df.test, ytest = y.test,ntree=500,mtry=ncol(df.train))
  
rf4<-randomForest(df.train, y.train,xtest = df.test, ytest = y.test,ntree=500,mtry=(ncol(df.train))/3)

rf5<-randomForest(df.train, y.train,xtest = df.test, ytest = y.test,ntree=500,mtry=(ncol(df.train))/4)

```

Now we are going to plot our trees.

```{r}
plot(1:500, rf1$mse,col="blue",type="l",xlab = "NoTrees", ylab = "MSE", ylim = c(10,25))
lines(1:500, rf2$mse, col="red", type="l")
lines(1:500, rf3$mse, col="green", type="l")
lines(1:500, rf4$mse, col="orange", type="l")
lines(1:500, rf5$mse, col="purple", type="l")
```

We can see that MSE decreases with the increase in number of trees and reaches
a halt after a certain point. This tells that we will see no improvement if we
increase the number of trees. However, how quickly that point is reached depends
on the number of columns we added to our model. Lastly, mtry greatly affects
which model reaches the lowest MSE.


