---
title: "Exercise 12, Chapter 3"
author: "Ntoulmperis Mixalis"
date: "20/05/2022"
output:
  ioslides_presentation:
    smaller: no
  beamer_presentation: default
---
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## (a) To start with we define our equations:
\
*Regression of Y onto X*
$$\hat{y} = \hat{β_a}x$$
\
*Regression of X onto y*
$$\hat{x} = \hat{β_b}y$$
\newpage

## For each of the previous equations the slope is defined as:
$$\hat{β_a}=\sum_{i = 1}^{n}\frac {xy}{x^2}$$
\
$$\hat{β_b}=\sum_{i = 1}^{n}\frac {yx}{y^2}$$
\newpage

## Finally, we find that :
\
\
\
\
\
$$\hat{β_a}=\hat{β_b} <=>\sum_{i = 1}^{n}\frac {xy}{x^2}=\sum_{i = 1}^{n}\frac {yx}{y^2} <=> \sum_{i = 1}^{n}x^2_i=\sum_{i = 1}^{n}y^2_i$$
\newpage

## (b) We build 2 models of Y on X and vice versa
```{r}
set.seed(2022)
x <- rnorm(100)
y <- 2*x + rnorm(100, sd = 2)
df0 <- data.frame(x, y)
lm.fit0 <- lm(y ~ x +0, data=df0)
lm.fit1 <- lm(x ~ y +0, data=df0)
par(mfrow = c(1,2))
```
\newpage
## Obviously the coefficient estimates are different.
```{r fig1, fig.height = 3, fig.width = 6}
plot(x, y, xlab = "Predictors", ylab= "Response")
abline(lm.fit0, lwd=3, col=5)
abline(lm.fit1, lwd=3, col=2)
```
\newpage

## (c) We try the same this but with a diffent formula for the model
```{r}
set.seed(2022)
x <- rnorm(100)
y <- x
df1 <- data.frame(x, y)
lm.fit2 <- lm(y ~ x + 0, data=df1)
lm.fit3 <- lm(x ~ y + 0, data=df1)
```
\newpage
## Obviously the coefficient estimates are the same.
```{r fig2, fig.height = 3, fig.width = 6}
plot(x, y, xlab = "Predictors", ylab= "Response")
abline(lm.fit2, lwd=3, col=5)
abline(lm.fit3, lwd=3, col=2)