---
title: "Ex.7Chapter8"
author: "Ntoulmperis Michail"
date: "26/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First we load the libraries and the assign the data set to "df"
```{r, warning = FALSE, message = FALSE}
library(tree)
library(ISLR2)
library(randomForest)
df <- Carseats
```

## Split the data
```{r}
set.seed(1)
train <-sample(1:nrow(df),nrow(df)*0.7)

df.train<-df[train,]
df.test<-df[-train,"Sales"]
```

## Build the model and plot the tree

```{r}
tree.df<-tree(Sales ~ ., data=df, subset = train)

summary(tree.df)

plot(tree.df)

text(tree.df,pretty=0)

```

## Prediction and MSE

```{r, message = FALSE}

 
tree.prediction <- predict(tree.df, newdata = df.train)

tree.mse <- mean((df.test - tree.prediction)^2)

tree.mse
```
As we can see the Mse is 13.1404

```{r}
set.seed(1)

tree.df<-tree(Sales ~ ., data=df, subset = train)


cv.df <- cv.tree(tree.df)

plot(cv.df$size,cv.df$dev,xlab = "Size of Tree",ylab = "Deviance",type = "b")


prune.predict<-predict(tree.df, df.test)

mean((prune.predict-df.test)^2)


```

We have used cross validation to find the size to which the tree should be 
pruned. The size for which the deviance is minimum is selected as the optimal 
size.

## Bagging

```{r}
set.seed(1)

bag.df<-randomForest(Sales ~ ., df.train,importance=TRUE,mtry=10)

importance(bag.df)


```

```{r}
bag.df.predict<-predict(bag.df, df.test)
mean((bag.df.predict-df.test)^2)

```
We use randomForest with m=p=10 total number of predictors which is equivalent
to bagging. We can see that Price and ShelveLoc are the most important
predictors.


```{r}
rf.df <- randomForest(Sales ~ .,df.train, importance=TRUE, mtry=sqrt(10))
importance(rf.df)


```

```{r}


rf.car.predict<-predict(rf.df, df.test)


mean((rf.car.predict-df.test)^2)

```
Using Random Forest the MSE increased compared to bagging, the important 
variables chosen by Random Forest are the same as the one chosen by Bagging
Random Forest avoids correlated trees and hence is expected to perform better
than Bagging, the results from our analysis are tend to show that Bagging in
this case is better.




